### 2015-11-03 CVPR16/Source/experiments.tex
Plotted RAS and Brox together by an inner join. Will plot with a outer join if time permitted.

%\begin{table}
%  \centering
%  \begin{tabular}{lccc}
%    \toprule
%    Algorithm & All & Unoccluded cars & Occluded cars \\
%    \midrule
%    bounding box only                         & $0.18\pm0.01$          & $\color{red}0.04\pm0.003$  & $0.41\pm0.04$\\
%    Using $\assocP{}$                         & $0.18\pm0.01$          & $0.05\pm0.003$           & $0.39\pm0.04$ \\
%    Using $P^{(ij)}_{\text{assoc by reproj}}$ & $0.18\pm0.01$          & $0.06\pm0.003$           & $0.39\pm0.04$\\
%    Using $P^{(ij)}_{\text{assoc}}$           & $\color{red}0.17\pm0.01$ & $0.05\pm0.003$           & $\color{red}0.38\pm0.04$\\
%    \bottomrule
%  \end{tabular}
%  \caption{Association Experiment results. The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence. }
%\end{table}
\begin{figure*}
  \includegraphics[width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence_static_and_dynamic.pdf}\\
  \includegraphics[width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence_occ_50.pdf}\\
  \includegraphics[width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence_50.pdf}\\
  \includegraphics[width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence_occ_50.pdf}
  \caption{From top: (1)Association Experiment results on all points. %} \label{fig:assoc-results}
    (2) Association Experiment results on occluded points. %} \label{fig:assoc-occ-results}
    (3) Association Experiment results on dynamic points. %} \label{fig:assoc-dynamic-results}
    (4) Association Experiment results on dynamic  and occluded points. The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence. } \label{fig:assoc-occ-results}
\end{figure*}

@@

\newpage
\newlength{\tblimgwidth}
\setlength{\tblimgwidth}{0.40\textwidth}
\begin{table*}
  \centering
  \begin{tabular}{ccc}
    & Assignments & Error in assignment\\
    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Brox} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Brox} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
  \end{tabular}
  \caption{Qualitative results for association experiment. The left column
  shows the point tracks assignment to appropriate track. Each color represents
a different track to which the point is associated to. Right column shows the
probablistic error in association: red is low error and blue is high error.
Note that our method changes smoothly at the boundary of the objects with
intermediate probabilities, while the baseline methods have only 0-1 error.} 
\end{table*}

>>>>

%\begin{table}
%  \centering
%  \begin{tabular}{lccc}
%    \toprule
%    Algorithm & All & Unoccluded cars & Occluded cars \\
%    \midrule
%    bounding box only                         & $0.18\pm0.01$          & $\color{red}0.04\pm0.003$  & $0.41\pm0.04$\\
%    Using $\assocP{}$                         & $0.18\pm0.01$          & $0.05\pm0.003$           & $0.39\pm0.04$ \\
%    Using $P^{(ij)}_{\text{assoc by reproj}}$ & $0.18\pm0.01$          & $0.06\pm0.003$           & $0.39\pm0.04$\\
%    Using $P^{(ij)}_{\text{assoc}}$           & $\color{red}0.17\pm0.01$ & $0.05\pm0.003$           & $\color{red}0.38\pm0.04$\\
%    \bottomrule
%  \end{tabular}
%  \caption{Association Experiment results. The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence. }
%\end{table}
\begin{figure*}
\includegraphics[trim=1.0in 0.2in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
  \caption{From top: (1)Association Experiment results on all points. %} \label{fig:assoc-results}
    (2) Association Experiment results on occluded points. %} \label{fig:assoc-occ-results}
    (3) Association Experiment results on dynamic points. %} \label{fig:assoc-dynamic-results}
    (4) Association Experiment results on dynamic  and occluded points. The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence. } \label{fig:assoc-occ-results}
\end{figure*}

@@

\newpage
\newlength{\tblimgwidth}
\setlength{\tblimgwidth}{0.40\textwidth}
\begin{table*}
  \centering
  \begin{tabular}{ccc}
    & Associations & Error in association\\
    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Brox} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Brox} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
  \end{tabular}
  \caption{Qualitative results for association experiment. The left column
  shows the point tracks assignment to appropriate track. Each color represents
a different track to which the point is associated to. Right column shows the
probablistic error in association: red is low error and blue is high error.
Note that our method changes smoothly at the boundary of the objects with
intermediate probabilities, while the baseline methods have only 0-1 error.} 
\end{table*}
